He-Man: A domain-specific language for lightweight concurrency

### 2011-12-13 report/report.tex
Finish up front-end

%We also provide an \b{Assign} wrapper that takes a \t{Prog Expr} as its argument

@@

>>>>

Although the He-Man target language does not support defining
functions, code modularity and reuse is easily supported while writing
He-Man code by defining Haskell functions that produce values in
\t{Prog}. When invoked, the code of these meta-level ``functions'' is
included directly at the call-site. This is a very powerful tool, but
can potentially result in code size explosion if used carelessly.

As an example of the power that Haskell and the monadic style gives
us, Figure \ref{fig:generic} shows our library routines for simulating
blocking network operations. \t{do\_nb\_action} takes an event
\t{Expr} and a \t{Prog Expr} action representing a network call that
can return \t{EAGAIN} and produces an action that generates code to
simulate a blocking network operation. This allows us to describe how
to simulate blocking I/O in a generic way, and then invoke it to
create our concrete wrappers.
(\t{.=.} is a wrapper for
\b{Assign} that takes a \t{Prog Expr} as its second argument and the
\t{sock\_*} functions invoke \b{Call} wrappers on the appropriate
network calls).

@@

\begin{figure}[ht]
\centering
\begin{smallverbatim}
do_nb_action :: Expr -> Prog Expr -> Prog Expr
do_nb_action e action = do
  res <- action
  ifthen (res .< 0) $ do
    while (res .< 0) $ do
      wait e
      res .=. action
  return res

accept (fd, e) =
  do_nb_action e (sock_accept fd)
do_read (fd, e) buf size =
  do_nb_action e (sock_read fd buf size)
do_write (fd, e) buf size =
  do_nb_action e (sock_write fd buf size)
\end{smallverbatim}
\caption{Implementation of ``blocking'' network calls}
\label{fig:generic}
\end{figure}
